---
title: "Untitled"
author: "Andres"
date: "2023-02-27"
output: html_document
---

```{r}

library(nycflights13)
library(tidyverse)
library(ggplot2)
Bd <- nycflights13::flights

```

## R Markdown



```{r}
R2 <- RetrasoMas2Horas()
ggplot(data = R2, aes(x = carrier)) +
geom_bar() +
ggtitle("Aerolíneas con más vuelos retrasados") +
xlab("Aerolínea") +
ylab("Cantidad de vuelos retrasados")
```
```{r}
Vh <- VuelosHouston()
ggplot(data = Vh, aes(x = carrier)) +
geom_bar() +
ggtitle("Vuelos a Houston") +
xlab("Aerolínea") +
ylab("Cantidad de vuelos")
```
```{r}
Op <- VoperadosUUAUDL()
ggplot(data = Op, aes(x = carrier)) +
geom_bar() +
ggtitle("Vuelos operados por United, American y Delta") +
xlab("Aerolínea") +
ylab("Cantidad de vuelos")
```
```{r}
Sv <- SalidaVerano()
ggplot(data = Sv, aes(x = carrier)) +
geom_bar() +
ggtitle("Vuelos que salieron en verano") +
xlab("Aerolínea") +
ylab("Cantidad de vuelos")
```
```{r}
R1h <- RetrasoAlM1hora()
ggplot(data = R1h, aes(x = carrier)) +
geom_bar() +
ggtitle("Vuelos que se retrasaron al menos una hora") +
xlab("Aerolínea") +
ylab("Cantidad de vuelos")
```
```{r}
Ve12To6 <- Vuelos12To6()
ggplot(data = Ve12To6, aes(x = carrier)) +
geom_bar() +
ggtitle("Vuelos que salierón entre la medianoche y las 6 a. m.") +
xlab("Aerolínea") +
ylab("Cantidad de vuelos")
```

# Example 1 We will select flights that departed between 6 and 8 am:

```{r}
Between1 <- Bd %>%
filter(between(hour, 6, 8))

```
The new Dataset is as follows

```{r}
Between1 
```

# Example 2 We will select flights departing in May or June:

```{r}
Between2 <- Bd%>%
  filter(between(month, 5, 6))
```
The new Dataset is as follows

```{r}
Between2 
```

# Example 3 We will select flights that arrived on time (i.e. no delays):

```{r}
Between3 <- Bd %>%
  filter(between(arr_delay, -1, 0))
```
The new Dataset is as follows

```{r}
Between3
```

#Example 4 We will select flights that arrived on time (i.e. no delays):

```{r}
Between4 <- Bd %>%
  filter(between(dep_delay, 1, 30) & between(arr_delay, 31, Inf))
```
The new Dataset is as follows

```{r}
Between4 
```

# Example 5 We will select flights that arrived on time (i.e. no delays):

```{r}
Between5 <- Bd %>%
  filter(between(dep_delay, 1, 30) & between(arr_delay, 31, Inf))
```
The new Dataset is as follows

```{r}
Between5
```
